---
title: "Homework 6"
author: "Yuan Meng"
date: "12/3/2021"
output: github_document
---

```{r, message=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(patchwork)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

### Data Cleaning

```{r message=FALSE}
birth_weight= read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace)) %>% 
  mutate(babysex = recode(babysex,"1" = "male","2" = "female"),
         frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other",                        "9" = "Unknown"),
         malform = recode(malform, "0" = "absent", "1" = "present"),
         mrace = recode(mrace, "1" = "White", "2"= "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other"))
```

### check missing data

```{r}
 birth_weight %>% 
  skimr::skim() %>% 
  select(skim_variable, n_missing)
```

There is no missing values in the data set. 

### Regression

```{r}
weight_fit = 
  birth_weight  %>% 
  lm(bwt ~ momage + smoken + ppbmi + fincome, data = .)  #proposed model
```
I proposed that baby’s birth weight associated with `fincome` (family income), `momage` (mother's age at delivery), `smoken` average number of cigarettes smoked per day during pregnancy and `ppbmi`mother’s pre-pregnancy BMI. 

```{r}
 birth_weight %>% 
  modelr::add_residuals(weight_fit) %>% 
  modelr::add_predictions(weight_fit) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point()+
  geom_smooth(se = FALSE, method = lm)
```

### Other two models

Using length at birth and gestational age as predictors (main effects only)
```{r}
weight_fit = 
  birth_weight %>% 
    lm(bwt ~ momage + smoken + ppbmi + fincome, data = .)  #proposed model
```

```{r}
weight_fit %>% 
   broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
birth_weight %>% 
  lm(bwt ~ bhead + blength + babysex + bhead*blength 
                 + bhead*babysex + blength*babysex + bhead*blength*babysex, 
                 data = .) %>%
  broom::tidy() 
```

```{r}
cv_df = 
  crossv_mc(birth_weight, 100) 
```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    my_model_fit  = map(train, ~lm(bwt ~ momage + smoken + ppbmi + fincome, data =  birth_weight)),
    fit_mod1  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit_mod2  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength 
                 + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_my_model = map2_dbl(my_model_fit, test, ~rmse(model = .x, data = .y)),
    rmse_mod1 = map2_dbl(fit_mod1, test, ~rmse(model = .x, data = .y)),
    rmse_mod2 = map2_dbl(fit_mod2, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y =rmse, fill = model)) + geom_violin(alpha = .5) + 
  geom_boxplot(alpha = .3) +
  labs(
    y = "RMSE",
    x = "Models"
  )
```

The model2 have the lowest RMSE, so it is the best model. 

## Problem 2

```{r message = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


### R.squared

```{r}
r_squared = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax~tmin, data = .x)),
    results = map(models, broom::glance)
  ) %>% 
  select(-models, -strap) %>% 
  unnest(results) 

```


```{r}
r_squared %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025),
    ci_upper = quantile(r.squared, 0.975)
  )
```

### R.squared Plot

```{r}
r_squared %>% 
  ggplot(aes(x = r.squared)) + 
   geom_density() 

mean_r_squared = r_squared %>%
  pull(r.squared) %>% 
  mean()
mean
```
 
The plot appears to be normally distributed and mean is 0.911, which with a 95% Confidence Interval (0.894, 0.927).
 
### Log value 

```{r}
log_data = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax~tmin, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-models, -strap) %>%
  unnest(results)
```


```{r}
log_result = 
  log_data  %>% 
  select(term, estimate) %>% 
  pivot_wider(names_from = term, 
              values_from = estimate,
              values_fn = list
              ) %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  mutate(log_beta = log(intercept*tmin))
```

```{r}
log_result %>% 
  summarize(
    ci_lower = quantile(log_beta, 0.025),
    ci_upper = quantile(log_beta, 0.975)
  )
```

### Log value Plot

```{r}
log_result %>% 
  ggplot(aes(x = log_beta))+  
  geom_density()

mean_log = 
  log_result %>%
  pull(log_beta) %>% 
  mean()
mean_log
```

The plot appears to be normally distributed and mean is 2.01, which with a 95% Confidence Interval (1.965, 2.059).